\documentclass{article}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{lipsum}
\usepackage[top=30mm, bottom=30mm, left=20mm, right=20mm]{geometry}

% Define section format
\titleformat{\section}
  {\normalfont\Large\bfseries}{\thesection}{1em}{}

% Remove section numbering
\setcounter{secnumdepth}{0}

% Define new list for objectives
\newlist{aims}{enumerate}{1}
\setlist[aims]{label=\textbf{\arabic*.},leftmargin=*}

\begin{document}

\noindent \textbf{\huge BYE LAWS}

\vspace{5mm}

\section{Club Name \& Purpose}

\noindent \textbf{Name:} The club shall be known as TechnoClub.

\noindent \textbf{Purpose:} TechnoClub is dedicated to the following objectives:

\begin{aims}
\item Equipping science students with essential engineering skills.
\item Training members in cutting-edge technologies such as AutoCAD, Simulation, Programming, Arduino/Raspberry Pi.
\item Fostering innovation by guiding students to independently create projects.
\item Encouraging technological self-sufficiency for national progress.
\item Promoting cross-disciplinary learning and collaboration.
\end{aims}

\vspace{5mm}

\section{Membership \& Dues}

\noindent \textbf{Eligibility:} All students attending the University of Hyderabad are eligible for membership.

\vspace{5mm}

\section{Officer Bearers}

\noindent \textbf{Officers:} The club will have a President, Vice-President, Secretary, and Treasurer.

\noindent \textbf{Eligibility:} Officers must be active members of TechnoClub.

\noindent \textbf{Election:} Officers will be elected annually by a majority vote.

\noindent \textbf{Term:} Officers will serve for one year, beginning at the start of the spring semester.

\noindent \textbf{Vacancy:} In case of a vacancy in the Presidency, the Vice-President will assume the role for the remainder of the term. Vacancies in other offices will be filled by a special election.

\vspace{5mm}

\section{Duties of Officers}

\noindent \textbf{President:} The President is responsible for running meetings, voting only in case of a tie, representing the club, appointing committee chairpersons (subject to Executive Committee approval), and serving as an ex-officio member of all committees except the nominating committee.

\noindent \textbf{Vice-President:} The Vice-President runs meetings in the President's absence and serves as chairperson of the Program Committee.

\noindent \textbf{Secretary:} The Secretary records meeting minutes, maintains club records, keeps a current membership roster, issues meeting notices, and manages the club's general correspondence.

\noindent \textbf{Treasurer:} The Treasurer receives all funds and processes Request for Payment, Deposit Slip, and Officer Signature Forms.

\vspace{5mm}

\section{Aims \& Objectives}

\begin{aims}
\item Impart essential engineering skills to science students at the university.
\item Train club members in new-age technology relevant to their domains such as AutoCAD, Simulation tools, Programming, Arduino/Raspberry Pi etc.
\item Provide a platform for students to innovate and implement their own projects from scratch.
\item Inspire students towards achieving technological self-sufficiency for national progress.
\item Foster interdisciplinary learning and research by exposing students from various backgrounds to related fields.
\end{aims}

\vspace{5mm}

\noindent This document was last updated on \today.

\vspace{5mm}
\end{document}
